The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-09-09 paper/Analisis.tex
updated section 2

\section{Modeling Bulk Gas Rotation}
\label{sec:implementation}

@@

 In the MonteCarlo code we define a cartesian coordinate system to
 define the position of each photon. The origin of this system
 coincides with the center of the sphere and the rotation axis is defined
 to be $z$-axis. With this choice, the components of the gas bulk velocity
 field, $\vec{v} = v_{x}\hat{i} + v_{y}\hat{j} + v_{z}\hat{k}$, can be
 written as

@@

In contrast with spherically symmetric models (static, outflow,
inflow) the rotation now defines a preferred direction in the
problem. In Section \ref{sec:results} we quantify this differences by
varying the line of sight of a mock observer with respect to the
rotation axis. The results are parametrized by the polar angle
$\theta$ as defined by the dot product $\cos\theta =
{\hat{u}\cdot\hat{k}}$.

@@

In the Monte Carlo calculations we follow the propagation of $N_{\gamma}=10^5$
numerical photons through different spherical galaxies. Each galaxy
model varies at least one of the following parameters: the maximum
rotational velocity $V_{\rm max}$, the hydrogen optical depth $\tau_{H}$,
the dust optical depth $\tau_{a}$ and the initial distribution of photons
with respect to the gas. There are in total 60 models combining all
the input parameters summarized in Table \ref{table:models}.

We have used two independently developed Monte Carlo codes
\citep{CLARA,DijkstraKramer} to perform the calculations of the
non-dusty models. The results we report here are robust in the sense
that they are obtained by both codes.

\begin{table}
\begin{center}
\begin{tabular}{llc}\hline\hline
Physical Parameter (units) & Symbol & Values\\\hline
Velocity (\kms) & $V_{\rm max}$&$0,\ 50,\ 100,\ 200,\ 300$\\
Hydrogen Optical Depth & $\tau_{H} $ & $10^{5},\ 10^{6},\ 10^{7}$\\
Dust Optical Depth & $\tau_{a}$ & $0$,$1$\\
Photons Distributions & & Central, Homogeneous\\\hline\hline
\end{tabular}
\caption{
  List of the physical parameters that define the spherical models 
  imulated using Monte Carlo calculations. For each parameter we
  vary the values in the range listed in the last column. Takig into
  account all the possible combinations we end up with $60$ different
  models. } 
\label{table:models}
\end{center}
\end{table}

>>>>

\section{Models of bulk gas rotation}
\label{sec:implementation}

@@

 In the MonteCarlo code we define a cartesian coordinate system to
 describe the position of each photon. The origin of this system
 coincides with the center of the sphere and the rotation axis is defined
 to be $z$-axis. With this choice, the components of the gas bulk velocity
 field, $\vec{v} = v_{x}\hat{i} + v_{y}\hat{j} + v_{z}\hat{k}$, can be
 written as

@@

For each photon in the simulation we have its initial position inside
the sphere, direction of propagation $\hat{k}_{in}$ and reduced
frequency $x_{in}$. The photon's propagation stops once they cross the
surface of the sphere. At this point we store the position, the outgoing direction
of propagation $\hat{k}_{out}$ and the reduced frequency $x_{out}$. We
define the angle $\Theta$ by $\cos\Theta = \hat{k}\cdot
\hat{k}_{out}$, that is the polar angle of the outgoing photon with
respect to the $z$ axis. Following \cite{Zheng2013} we make the study
of the anisotropic emission in terms of this angle $\Theta$.

@@

In the Monte Carlo calculations we follow the propagation of $N_{\gamma}=10^5$
numerical photons through different spherical galaxies. For each galaxy
we vary at least one of the following parameters: the maximum
rotational velocity $V_{\rm max}$, the hydrogen optical depth $\tau_{H}$,
the dust optical depth $\tau_{a}$ and the initial distribution of photons
with respect to the gas. There are in total $60$ models combining all
the input parameters. Table \ref{table:models} presents a summary of
all the models.

Additionally, we have used two independently developed Monte Carlo
codes \citep{CLARA,DijkstraKramer} to perform the calculations of the
non-dusty models. The results we report here are robust in the sense
that they are obtained by both codes.

\begin{table}
\begin{center}
\begin{tabular}{llc}\hline\hline
Physical Parameter (units) & Symbol & Values\\\hline
Velocity (\kms) & $V_{\rm max}$&$0,\ 50,\ 100,\ 200,\ 300$\\
Hydrogen Optical Depth & $\tau_{H} $ & $10^{5},\ 10^{6},\ 10^{7}$\\
Dust Optical Depth & $\tau_{a}$ & $0$,$1$\\
Photons Distributions & & Central, Homogeneous\\\hline\hline
\end{tabular}
\caption{
  List of the physical parameters that define the spherical models 
  simulated in our Monte Carlo calculations. For each parameter we
  vary the values in the range listed in the last column. Takig into
  account all the possible combinations we end up with $60$ different
  models.} 
\label{table:models}
\end{center}
\end{table}
